Towards Compiler-Agnostic Performance in Finite-Difference Codes

### 2015-08-07 shallow_perf.tex
small update for psykal approach

%Proliferation of lightweight cores is resulting in increased
%complexity in the programming models required to achieve performance.
%Combine with the complexity of e.g. a model simulating circulation in
%the global ocean. Significant challenge in software engineering.
%Propose an approach for meeting this challenge by separating the
%computational science demands from the {\it e.g.} oceanographic
%demands.

The \psykal approach separates code into three layers; the Algorithm
layer, the PSy layer and the Kernel layer. While this approach is
general, we are currently applying it to Atmosphere and Ocean models
written in Fortran where domain decomposition is typically performed
in the latitude-longitude direction, leaving columns of elements on
each domain-decomposed partition.

@@

This work made use of the ARCHER UK National Supercomputing Service
(\url{http://www.archer.ac.uk}). We acknowledge use of the Hartree
Centre IBM Power 8 system in this work. The STFC Hartree Centre is a
research collaboratory in association with IBM providing High
Performance Computing platforms funded by the UK's investment in
e-Infrastructure. The Centre aims to develop and demonstrate next
generation software, optimised to take advantage of the move towards
exa-scale computing. This work was funded by NERC project {\bf xxx}

>>>>

The \psykal approach attempts to address the problems described in the
previous section. It separates code into three layers; the Algorithm
layer, the PSy layer and the Kernel layer. The approach has been
developed in the GungHo project~\cite{GungHo}, which is creating a new
Dynamical core for the Met Office, and its design has been influenced
by earlier work on OP2~\cite{OP2,PYOP2}.

While this approach is general, we are currently applying it to
Atmosphere and Ocean models written in Fortran where domain
decomposition is typically performed in the latitude-longitude
direction, leaving columns of elements on each domain-decomposed
partition.

@@

This work made use of the ARCHER UK National Supercomputing Service
(\url{http://www.archer.ac.uk}). We acknowledge use of the Hartree
Centre IBM Power 8 system in this work. The STFC Hartree Centre is a
research collaboratory in association with IBM providing High
Performance Computing platforms funded by the UK's investment in
e-Infrastructure. The Centre aims to develop and demonstrate next
generation software, optimised to take advantage of the move towards
exa-scale computing. This work was funded by the NERC `GOcean' project,
grant number NE/L012111/1.
